Geometric variational problems

### 2020-11-11 NSF2020/Description/background.tex
rjr

\noindent
{\bf Collaborative Research: Mathematical modeling and simulations of
self-assembling amphiphilic particles in a solvent} \\
%{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
FSU), and Y.-N. Young (PI, NJIT)}
\section{Background}
\label{sec:background}
The goal of this collaborative proposal is to use continuum modeling and
numerical simulations to investigate the dynamic self-assembly of
amphiphilic particles interacting with each other via hydrophobic forces
in a solvent. Amphiphilic particles (such as lipid molecules) possess
both hydrophobic and hydrophilic structures. In a viscous solvent they
self-assemble into meso-/macroscopic structures (such as micelles and
bilayers of lipids) to shield their hydrophobic parts from contact with
the solvent molecules (water).
%
%\subsection{Hydrophobic Forces}
%\label{sec:hydrophobicforce}
%
Such self-assembly of amphiphiles via hydrophobic force is ubiquitous in biology and biophysics \cite{Israelachvili1954},
%The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
and has been a major source of nonspecific interactions between
nanoparticles for self-assembly in  soft matter
\cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

@@

The substantial free energy for placing hydrophobic substances in contact with water 
is roughly proportional to the surface area of the contact region \cite{Bjorneholm2016}.  
%As a result, hydrocarbon solutes have a large interfacial tension 
%and try to minimize their surface area when in water. 
At the microscopic level, the hydrophobic force is a long-range, surface
interaction.  This means that two hydrophobic surfaces, separated by
water over some distance, experience an attractive force
\cite{Lum1999,Meyer2006,Hammer2010}.  Measurements show that the
hydrophobic force decays exponentially with a decay length like 1 nm
\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is
also known that the interaction is not pairwise additive, meaning that
the force between any two hydrophobic objects is altered by the presence
of a third  object.

@@

The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles.
These results will facilitate optimal designs of smart materials of desirable properties by
tuning the geometry and properties of the amphiphilic particles.

>>>>

\noindent
{\bf Collaborative Research: Mathematical modeling and simulations of
self-assembling amphiphilic particles in a solvent} \\
%{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
FSU), and Y.-N. Young (PI, NJIT)}
\section{Background}
\label{sec:background}
The goal of this collaborative proposal is to use mathetical modeling and
numerical simulations to investigate the dynamic self-assembly of
amphiphilic particles interacting with each other via hydrophobic forces
in a solvent. Amphiphilic particles (such as lipid molecules) possess
both hydrophobic and hydrophilic structures. In a viscous solvent they
self-assemble into meso-/macroscopic structures (such as micelles and
bilayers of lipids) to shield their hydrophobic parts from contact with
the solvent molecules (water).
%
%\subsection{Hydrophobic Forces}
%\label{sec:hydrophobicforce}
%
Such self-assembly of amphiphiles via hydrophobic force is ubiquitous in biology and biophysics \cite{Israelachvili1954},
%The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
and has been a major source of nonspecific interactions between
nanoparticles in  soft matter
\cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

@@

The substantial free energy for placing hydrophobic substances in contact with water 
is roughly proportional to the surface area of the contact region \cite{Bjorneholm2016}.  
%As a result, hydrocarbon solutes have a large interfacial tension 
%and try to minimize their surface area when in water. 
At the microscopic level, the hydrophobic force is a long-range, surface
interaction.  This means that two hydrophobic surfaces, separated by
water over some distance, experience an attractive force
\cite{Lum1999,Meyer2006,Hammer2010}.  Measurements show that the
hydrophobic force decays exponentially with a decay length like 1 nm
\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is
also known that the interaction is not pairwise additive, meaning that
the force between any two hydrophobic objects is altered by the presence
of a third, hydrophobic or otherwise, object \cite{SilveraBatista1242477}.

@@

The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
tuning the geometry and properties.
